Combinatorial interpretations of~holonomic recurrences

### 2021-09-13 article/main.tex
Minor fix
Fix bB in UB

\begin{interpretation}
Let's translate the recurrence to the bijective language.
\begin{itemize}
    \item \(b_n\) is simply the set of all full binary trees of size \(n\),
    \item \((n + 2) b_{n + 1}\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
    \item \((2n + 1) b_{n}\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a~leaf) pointed (i.e.~distinguished),
    \item \(2\) at the beginning of \(2 (2n + 1) b_{n}\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
\end{itemize}

@@

We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with a~single node pointed. For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\). Therefore we generate \(2(2n + 1) B(n)\) trees of size \(n + 1\).
\todo{rewrite}

The only thing that's left for us to verify is if we generate all trees of size \(n + 1\) with pointed leaves. As from the recursion, we know that \(2 (2n + 1) B(n)\) is total number of trees with single leaf pointed, it is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\). It can happen in 2 ways:
\begin{enumerate}
    \item operation itself generates duplicates or
    \item 2 different operations generate the same tree.
\end{enumerate}

@@

An example of transformation we would like to add can be:

>>>>

\begin{interpretation}
Let's translate the recurrence to the bijective language.
\begin{itemize}
    \item \(B(n)\) is simply the set of all full binary trees of size \(n\),
    \item \((n + 2) B(n + 1)\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
    \item \((2n + 1) B(n)\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a~leaf) pointed (i.e.~distinguished),
    \item \(2\) at the beginning of \(2 (2n + 1) B(n)\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
\end{itemize}

@@

We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with a~single node pointed. For each of such trees, namely \(T\), we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\). Therefore we generate all trees from \(2(2n + 1) B(n)\).
\todo{rewrite}

The only thing that's left for us to verify is if we generate all trees of size \(n + 1\) with pointed leaves. As from the recursion, we know that \(2 (2n + 1) B(n)\) describe trees with single leaf pointed, it is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\). It can happen in 2 ways:
\begin{enumerate}
    \item operation itself generates duplicates or
    \item 2 different operations generate the same tree.
\end{enumerate}

@@

An example of transformation we may want to add can be:
